Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-04-09 ident_manu.Rnw
better schematic added
cover letter added

\documentclass[preprint]{elsarticle}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage{lineno}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage{paralist}
\usepackage{bm}
\usepackage{fixltx2e}
% \usepackage[inline]{showlabels}

@@

\linespread{1.5}

@@

\begin{document}

@@

This study describes a parameter sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.  The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifiability constraints.  The specific goals were to \begin{inparaenum}[1\upshape)]
\item identify the parameters that have the greatest influence on state variables using local sensitivity analysis,
\item quantify the identifiability of subsets of the total parameter space based on sensitivity,
\item and provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories.
\end{inparaenum}
The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model precision.  Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability the results. In addition to \ac{do}, other state variables that were evaluated included ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus. In general, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the complete parameter set can be optimized.

>>>>

\documentclass[review]{elsarticle}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage{lineno}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage{paralist}
\usepackage{bm}
\usepackage{fixltx2e}
% \usepackage[inline]{showlabels}

@@

\linespread{2}

@@

\begin{document}
\large

@@

This study describes a sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.  The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifiability constraints.  The specific goals were to \begin{inparaenum}[1\upshape)]
\item identify the parameters that have the greatest influence on state variables using local sensitivity analysis,
\item quantify the identifiability of subsets of the total parameter space based on sensitivity,
\item and provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories.
\end{inparaenum}
The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model precision.  Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability the results. In addition to \ac{do}, other state variables that were evaluated included ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus. In general, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the complete parameter set can be optimized.

### 2017-04-09 ident_manu.tex
cover letter added

\documentclass[preprint]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Tue Mar 28 17:29:18 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/55035672775b152721843109c2926082eceeba21}{55035672775b152721843109c2926082eceeba21}}

>>>>

\documentclass[review]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\large

@@

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Wed Mar 29 18:01:37 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/82b584d191ce9aa05d1adeff4e6db4a8a38db9e2}{82b584d191ce9aa05d1adeff4e6db4a8a38db9e2}}
